Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
Include year in Table 1 and fit on page

```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
journal <-
  tabyl(rrpp, journal) %>%
  select(-percent)

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>% 
  rename(Journal = journal,
         `5 Year IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  autofit() %>%
  set_caption(
    "Journal titles selected for inclusion, their respective five-year impact factors as of 2022 (5 Year IF) and the number (n) of articles from each journal that were evaluated."
  )
```

>>>>

```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
journal <-
  tabyl(rrpp, journal, year) %>%
  rowwise() %>%
  mutate(n = sum(c_across(where(is.numeric)), na.rm = T))

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>%
  rename(Journal = journal,
         `IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  fontsize(size = 10, part = "body") %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  set_caption(
    "Journal titles selected for inclusion, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
  )
```
